A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-01 mt-marathon.2013/PBML_article.tex
mv
start adding bibs

\title{A Comparison of the Synchronous-CFG \titlelinebreak{} Decoder Implementations}

@@

\begin{abstract}
Best practises for developing a SMT decoder has progressed enormously since the initial release of the Moses decoder in 2006. The emergence of syntax-inspired models, sparse features and more features, have been the driver for the major changes in the framework of the decoder.

@@

The open-source community has also changed from the dominance of phrase-based model and virtual Moses monopoly, to a situation where syntactic models are leading the research agenda, and other projects such as cdec and Joshua have equal prominance.
We take this opportunity to compare the implementations of these other decoders with Moses. We find that there are many similarities between the decoders, but also some surprising differences in implementation of even very fundamental features in each decoder.

@@

The Moses decoder was initially created for the phrase-based model. It was a vast improvement over its immediate predecessor, Pharoah, in being extensible. It allowed phrase-tables and language models. It allowed multiple phrase-table and language model implementations. The first has enabled researchers to combine multiple datasets in novel ways, as well as the use of secondary models on linguistic information (???). The second has spurred on improvements in the implementation of language models and phrase tables, which are ever faster, while using less memory (RandLM, KenLM, Compact PT).

>>>>

\title{A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations}

@@

\begin{abstract}
Best practise for developing a SMT decoder has progressed enormously since the initial release of the Moses decoder in 2006. The emergence of syntax-inspired models, sparse features and more features, have been the driver for the major changes in the framework of the decoder.

@@

The open-source community has also changed from the dominance of phrase-based model and virtual Moses monopoly, to a situation where syntactic models are leading the research agenda, and other projects such as cdec and Joshua have equal prominence.
We take this opportunity to compare the implementations of these other decoders with Moses. We find that there are many similarities between the decoders, but also some surprising differences in implementation of even very fundamental features in each decoder.

@@

In terms of extensibility, the Moses\cite{koehn-EtAl:2007:PosterDemo} decoder was a vast improvement over its immediate predecessor, Pharoah\cite{Koehn:Pharaoh:2004}.

Moses allows multiple phrase-tables and language models instances and implementations. The first has enabled researchers to combine multiple datasets in novel ways, as well as the use of secondary models on linguistic information\cite{Koehn:Philipp:2007, Sennrich:Rico:2011,Koehn:Philipp:2012}. The second has spurred on improvements in the implementation of language models and phrase tables, which are ever faster, while using less memory (RandLM, KenLM, Compact PT).
